Centralized Programming for Distributed Control Planes

### 2016-01-26 paper/compilation.tex
making edit pass

Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies. The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level languae into the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines the PGIR for the policy is safe, the compiler uses a simple translation to an abstract BGP (ABGP) representation. To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form. Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.

@@

The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints. Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}. Our regular expression language differs from others by allowing operators to describe preferences between paths.

@@

The syntax for the RIR is shown in Figure~\ref{fig:rir-syntax}. A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths. Regular paths are simply regular expressions where the base characters are AS numbers. Special \textit{in} and \textit{out} symbols are used to refer to any internal or external location respectively.
For example, the constraint
$$prefix=74.125.28.0/24 \mapsto (AS200 \cdot in \cdot in^*) \gg (AS100 \cdot in \cdot in^*)$$
describes a more-preferred set of paths for traffic announced by a prefixes no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

\sysname also supports constraints purely on the control-plane behavior of the BGP routing protocol. Thing like prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn. Aggregation, for example from internal locations and external locations, is specified using the same regular syntax as before:
$$agg(128.17.0.0/16, in \rightarrow out)$$
where the expression $in \rightarrow out$ refers to control messages flowing from any internal location to any external location.

We list the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, however our implementation also supports other constraints such as limiting the maximum number of routes, or enabling BGP multipath.

@@

The main differences between \sysname the regular language are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to be used locally.

@@

The next step is to rewrite the high-level constraints such as \textit{enter} and \textit{exit} according to the equivalences listed in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the top level for RIR, the final step is to lift the preferences that occur in the regular expression. For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$ by distributing the preference over the sequence operator. In general, we employ the follwing equivalence:
%
$$x \odot (y_1 \gg \dots \gg y_n) = x \odot y_1 \gg \dots \gg x \odot y_n$$
%
where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are flagged by the compiler as invalid policies.

@@

% Formally define automata
The translated user policy into RIR is of the form $r_1 \gg \dots \gg r_j$. While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., router advertisements flowing in the opposite direction). To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression. Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all internal and external ASes, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
%
% Formally define product graph
The combined product graph is a tuple: ($V'$, $E'$, $s$, $e$, $A$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon 2^{V' \times V'}$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and an preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to the sets of preferences.
For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. We say a node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.

% Formal product construction
Let $a_i$ and $b_i$ stand for states in the policy automata.
The product graph is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i \vert a_i \in F_i} $. That is, it records which preferences are achieved for the policy automata for each node in the product construction.
Finally, there is an edge from each node in the product graph such that $P(v) \neq \emptyset$ to the special end node $e$.

@@

Intuitively the product graph tracks which states of each automaton the policy is in as route advertisements move between routers in the topology.

Consider the topology shown in Figure~\ref{fig:example-compilation}. Suppose we want to set up a primary route from W that enters the network from $A$, and utilizes the A -- C and C -- D links. We also would like a backup route that enters from node $B$, and utilizes the B -- C link, but is otherwise unconstrained. For the sake of simplicity, we will assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(W \cdot A \cdot C \cdot D \cdot out) \gg (W \cdot B \cdot in^* \cdot out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
Figure~\ref{fig:example-compilation} shows the product graph obtained from intersecting the topology and policy automata. Every path in the product graph corresponds to a concrete path in the topology. In particular, every path through the product graph that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route advertisements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(1,1) X$. From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on. Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.

@@

Although every path through the product graph is a valid path in the topology, we do not want to consider loops when configuring the network. In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur.\footnote{Misconfigured aggregation can still lead to loops in BGP}
%
However, the product graph may contain many paths that form loops in the topology. For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid path that BGP route advertisements might take through the topology, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to avoid considering possibilities that are not possible due to loops. For example, if we can safely remove an edge from the product graph, then we don't have to consider what happens when the edge has failed.

@@

A node $x$ dominates node $y$ if $x$ appears on every path leading to $y$ from a source node. Many algorithms for finding graph dominators efficiently exist~\ref{bib:todo}. For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node. The following rules enable a cheap simplification of the product graph.
%
\begin{itemize}
  \item Remove nodes that never reach the end node
  \item Remove nodes not reachable from the $start$ node
  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
\end{itemize}
%
Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.

@@

The more challenging case is when a topology location occurs in mutliple contexts in the product graph. For example, the topology node $C$ can receive an advertisement from $E$ and later achieve the backup path, or it can receive an advertisement from its neighbor $D$ and later achieve either the primary or backup path. Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$? The important observation is that, if $C$ prefers $D$, then it is never worse off -- it will always achieve at least as good a path as if it had choosen $E$.
For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed. In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$. Since the $(3,2) C$ node has the same one-step and two-step next hops as node $(-,2) C$ in the product graph, no possible failure will prevent a route advertisment from reaching $(-,4) W$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and a simple enumeration of failures is intractable. Instead, we adopt a conservative analysis based on the product graph representation and the previous observations. The high-level idea is to order each node in the product graph according to a \textit{can prefer} relation. For example, node $(3,2) C$ can be preferred to node $(-,2) C$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted nodes that achieve preference $j$ or better, there are at least as the same paths as from $N_2$ restricted to $G_i$

@@

The algorithm listed in Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another. Intuitively, the algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step. Thus any paths leading from $N_2$ will have an equivalent path over the same topology locations from $N_1$. Algorithm~\ref{alg:failures} works because each node in the product graph can have at most one outgoing neighbor with the same topological location, so the next hop neighbors can be checked without backtracking. The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.

Local preferences are now obtained by, for each router in the topology, sorting the corresponding nodes in the product graph according to \textit{can prefer} relation. If two nodes are incomparable, then the compiler rejects the policy as unimplementable.

@@

The checks for failure safety described previously overlook one critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$. To avoid this situation, the compiler simply conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$). It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.

>>>>

Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies. The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level language into the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines the PGIR for the policy is safe, it uses a simple translation to an abstract BGP (ABGP) representation. To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form. Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.

@@

The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints. Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}. Our regular expression language differs from others by allowing operators to describe preferences between paths.

@@

The syntax for the RIR is shown in Figure~\ref{fig:rir-syntax}. A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths. Regular paths are simply regular expressions where the base characters are abstract locations - either a router or an Autonomous System (AS) number. Special \textit{in} and \textit{out} symbols are used to refer to any internal or external location respectively.
For example, the constraint
$$prefix=74.125.28.0/24 \mapsto (AS200 \cdot in^+) \gg (AS100 \cdot in^+)$$
describes a more-preferred set of paths for traffic announced by a prefixes no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $in^+$ stands for $in \cdot in^*$ in the usual way. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

\sysname also supports constraints purely on the control-plane behavior of the BGP routing protocol. Thing like prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn in practice. Aggregation, for example from internal locations and external locations, is specified using the same regular syntax as before:
$$agg(128.17.0.0/16, in \rightarrow out)$$
where the expression $in \rightarrow out$ refers to control messages flowing from any internal location to any external location.

We list the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, however our implementation also supports other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.

@@

The main differences between the \sysname front-end language and the RIR are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to be used locally.

@@

The next step is to rewrite the high-level constraints such as \textit{enter} and \textit{exit} according to the equivalences listed in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to lift occurences of the preference operator that occur in the regular expression. For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$ by distributing the preference over the sequence operator. In general, we employ the follwing equivalence:
%
$$x \odot (y_1 \gg \dots \gg y_n) = x \odot y_1 \gg \dots \gg x \odot y_n$$
%
where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are flagged by the compiler as invalid policies.

@@

% Formally define automata
The translated user policy into RIR is of the form $r_1 \gg \dots \gg r_j$. While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., router advertisements flowing in the opposite direction). To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression. Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all internal and external ASes, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
%
% Formally define product graph
The combined product graph is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon 2^{V' \times V'}$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. We say a node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$. That is, $x$ shadows $y$ when they are different nodes in the PGIR that represent the same topology location.

@@

% Formal product construction
Let $a_i$ and $b_i$ stand for states in the regular policy automata.
The product graph is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
%
Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
%
The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $. That is, it records which preferences are achieved for the policy automata for each node in the product construction.
%
Finally, there is an edge from each node in the product graph such that $P(v) \neq \emptyset$ to the special end node $e$.

Intuitively the product graph tracks which states of each automaton the policy is in as route advertisements move between routers in the topology.
%
Consider the topology shown in Figure~\ref{fig:example-compilation}. Suppose we want to set up a primary route from W that enters the network from $A$, and utilizes the A -- C and C -- D links. We also would like a backup route that enters from node $B$, and utilizes the B -- C link, but is otherwise unconstrained. For the sake of simplicity, we will assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(W \cdot A \cdot C \cdot D \cdot out) \gg (W \cdot B \cdot in^* \cdot out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
Figure~\ref{fig:example-compilation} shows the product graph obtained from intersecting the topology and policy automata. Every path in the product graph corresponds to a concrete path in the topology. In particular, every path through the product graph that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route advertisements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(1,1) X$. From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on. The $-$ state indicates it is dropped from the corresponding automaton. Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.

@@

Although every path through the product graph is a valid path in the topology, we do not want to consider loops when configuring the network. In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur.\footnote{Note: misconfigured aggregation can still lead to loops in BGP}
%
However, the product graph may contain many paths that form loops in the topology. For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid path that BGP route advertisements might take through the topology, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to avoid considering cases that are not possible due to loops. For example, if we can safely remove an edge from the product graph, then we don't have to consider what happens when the edge has failed.

@@

A node $x$ dominates node $y$ if $x$ appears on every path leading to $y$ from a source node. Many algorithms for finding graph dominators efficiently exist~\ref{bib:todo}. For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node. The following rules enable efficient minimization of the product graph.
%
\begin{itemize}
  \item Remove nodes that never reach the end node
  \item Remove nodes not reachable from the $start$ node
  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
\end{itemize}
%
Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.

@@

The more challenging case is when a topology location occurs in mutliple contexts in the product graph. For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ and later achieve the backup path, or it can receive an advertisement from its neighbor $D$ and later achieve either the primary or backup path. Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$? The important observation is that, if $C$ prefers $D$, then it is never worse off -- it will always achieve at least as good a path as if it had choosen $E$.
For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed. In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$. Since the $(3,2) C$ node has the same one-step and two-step next hops as node $(-,2) C$ in the product graph, no possible failure will prevent a route advertisment from reaching $(-,4) W$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and a simple enumeration of failures is intractable. Instead, we adopt a conservative analysis based on the product graph representation and the previous observations. The high-level idea is to order each node in the product graph according to a \textit{can prefer} relation. For example, node $(3,2) C$ can be preferred to node $(-,2) C$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted nodes that can potentially achieve preference $j$ or better, there are at least as many paths as from $N_2$ restricted to $G_i$

@@

The algorithm listed in Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another. The algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step. Thus any paths leading from $N_2$ will have an equivalent path over the same topology locations from $N_1$. Algorithm~\ref{alg:failures} works because each node in the product graph can have at most one outgoing neighbor with the same topological location, so the next hop neighbors can be checked without backtracking. The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.
\ryan{Add the new part that goes up to a dominating predecessor when no other option}

Local preferences are now obtained by, for each router in the topology, sorting the corresponding nodes in the product graph according to \textit{can prefer} relation. If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
\ryan{We are checking if the preorder forms a partial order by satisfying asymmetry}

@@

The checks for failure safety described previously overlook one critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$. To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$). It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
\ryan{rework this}

### 2016-01-26 paper/implementation.tex
making edit pass

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-sepcified aggregates. Users see only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.

@@

Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}. Our \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.

@@

Our compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}. More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better for large enough examples. However, we have not found minimization to be a bottleneck in our implementation. Minimization steps are ordered from cheapest to most expensive. All minimization steps are repeated until no more progress can be made.

@@

The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair in the product graph before minimization. Our implementation performs partial minimization during generation by recognizing cases where there is no restriction on exporting or importing from neighbors to avoid enumerating such cases.

>>>>

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-sepcified aggregates. Users only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.

@@

Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}. The \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.

@@

The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}. More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better suited for large enough topologies. However, we have not found minimization to be a bottleneck in our implementation. Minimization steps are ordered from cheapest to most expensive. All minimization steps are repeated until no more progress can be made.

@@

The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization. Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting or importing from neighbors.
